---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

require(webTRISr)
require(pixiedust)
require(magrittr)

```

# webTRISr

A R package for the WebTRIS Traffic Flow API, from Highways England. 

Feedback and contirubtions welcome - please raise and issue or pull request. 


## Installation 

```{r, eval=FALSE}
install.packages('devtools')
devtools::install_github('departmentfortransport/webTRISr')
```

## Examples
### Reports
Reports can be downloaded, as data frames, using `webtris_report()`
```{r, eval=FALSE}
webtris_report(sites=c('7', '24'), 
               start_date = '01012017', end_date = '01022017', 
               report_type = 'monthly-summary')
```


Note the data is cut here for easy printing, more variables are returned by the api. 
```{r, echo=FALSE}
x <- webtris_report(sites=c('7', '24'), 
               start_date = '01012017', end_date = '01022017', 
               report_type = 'monthly-summary') 

x[,1:6] %>% dust() %>%
  sprinkle(cols=1, halign = "left") %>%
  sprinkle_print_method("markdown")
```



All reports currently provided by the API are availble by changing the `report_type` argument. At present these options are: "daily", "annual-totals", "annual-monthly", "monthly-summary", "monthly-daily", "monthly-daily-aggregate", and "monthly-hourly-aggregate". 

### Areas

```{r, eval=FALSE}
webtris_areas()
```

```{r, eval=TRUE, echo=FALSE}
head(webtris_areas()) %>% dust() %>%
  sprinkle(cols=1, halign = "left") %>%
  sprinkle_print_method("markdown")
```


### Sites
```{r, eval=FALSE}
webtris_sites()
```

```{r, echo=FALSE}
head(webtris_sites())%>% dust() %>%
  sprinkle(cols=1, halign = "left") %>%
  sprinkle_print_method("markdown")
```

